Combining living and fossil taxa into phylogenies: the missing data issue

### 2014-06-11 Manuscript/TEM_draft.tex
Typo
Updated title
10/06 Updates (Results ML)

@@

%Title
\noindent{\Large \bf Effect of missing data in matrices containing living and fossil taxa on topological accuracy}
%Alternative punch title: "Bayesian method failure to infer topology using matrices containing both living and fossil taxa"
%Alternative punch title: "ML outperforms Bayesian for inferring topology from matrices containing both living and fossil taxa"
\bigskip

@@

\section{Results}
%Do the check for L00F00C00
\subsection{Building the trees}
Bayesian chains converged (SD $<$ 0.01 and ESS $>>$ 200 for each tree).
Good a quick convergence when using the sub-matrices especially for the "horizontal" sub-matrices.
Good enough phylogenetic signal.

\subsection{Comparing topologies}
Did it worked? See sub-matrices.

@@

\subsubsection{Effect of $M_L$}
In ML...(see Table ~\ref{Group_results})

Topological recovery was bad in Bayesian, the NTS score was only slightly above 0 which means that the mode of the RPBTC was only slightly different than expected by chance.
However, it seems that there is a small difference depending on the metric used.
For the Triples metric there is no significant effect of the $M_L$ parameter, in other words, if living taxa are removed, there is no effect on the placement of "flying" taxa.
For the Robinson-Fould metric, there is a significant effect of the $M_L$ leading small decrease in topological recovery when $M_L$ increases.
In other words, if living taxa are removed, clades are less conserved (see Table ~\ref{ML_results}).
However, in both cases, the effect of the parameter $M_L$ is still minimal compared to trees generated in a ML framework since the NTS score was only slightly higher than expected by chance (see Table ~\ref{Group_results}).

\subsubsection{Effect of $M_F$}
In ML...(see Table ~\ref{Group_results})

Similarly than for the effect of $M_L$, Bayesian tree recovery was only slightly better than expected by chance.
And in the same way as described above, there seems to be a small difference depending on the metric used.
There is no significant effect of the $M_F$ parameter when using the Triplet metric but the effect is significant when using the Robinson-Fould metric (see Table ~\ref{ML_results}).
However, as mentioned previously the effect of the parameter $M_F$ is still minimal in a Bayesian framework (see Table ~\ref{Group_results}).

\subsubsection{Effect of $M_C$}
In ML...(see Table ~\ref{Group_results})

The effect of $M_C$ in Bayesian framework is similar as the one described for $M_L$ and $M_F$: tree recovery is only slightly better than expected by chance and only the Robinson-Fould metric shows a significant effect of the $M_C$ parameter on tree recovery (see Table ~\ref{ML_results} and ~\ref{Group_results}).
\subsubsection{Combined effect}

In ML...(see Table ~\ref{Group_results})

In Bayesian, same pattern as above.
No particular effect of data combination, but more an effect of the overall amount of data (see Table ~\ref{Group_results}).

@@

The ability of recovering the best topology in maximum likelihood method is function of the amount of data missing.
However, in Bayesian, topology is badly (if not at all) recovered independently of the amount of data missing.

%Add the global heat plot figures
\begin{table}
\caption{Group difference per configuration set}
\centering
\begin{tabular}{rlrlccc}
    \hline
    set & metric & framework & parametric & $stats^1$ & df & p.value \\
    \hline
    $M_L$ & Robinson-Fould & ML & bla & bla & bla & bla \\
          &                & Bayesian & no & 65.62 & 4.00 & \textbf{0.00} \\
          & Triples & ML & bla & bla & bla & bla \\
          &         & Bayesian & no & 4.56 & 4.00 & 0.34 \\
    $M_F$ & Robinson-Fould & ML & bla & bla & bla & bla \\
          &                & Bayesian & no & 85.61 & 4.00 & \textbf{0.00} \\
          & Triples & ML & bla & bla & bla & bla \\
          &         & Bayesian & no & 3.01 & 4.00 & 0.56 \\ 
    $M_C$ & Robinson-Fould & ML & bla & bla & bla & bla \\
          &                & Bayesian & no & 64.23 & 4.00 & \textbf{0.00} \\
          & Triples & ML & bla & bla & bla & bla \\
          &         & Bayesian & no & 26.13 & 24.00 & 0.35 \\
    $M_L+M_F$ & Robinson-Fould & ML & bla & bla & bla & bla \\
              &                & Bayesian & no & 317.97 & 24.00 & \textbf{0.00} \\
              & Triples & ML & bla & bla & bla & bla \\
              &         & Bayesian & no & 3.01 & 4.00 & 0.56 \\ 
    $M_L+M_C$ & Robinson-Fould & ML & bla & bla & bla & bla \\
              &                & Bayesian & no & 290.10 & 24.00 & \textbf{0.00} \\
              & Triples & ML & bla & bla & bla & bla \\
              &         & Bayesian & no & 22.19 & 24.00 & 0.57 \\ 
    $M_F+M_C$ & Robinson-Fould & ML & bla & bla & bla & bla \\
              &                & Bayesian & no & 385.96 & 24.00 & \textbf{0.00} \\
              & Triples & ML & bla & bla & bla & bla \\
              &         & Bayesian & no & 20.23 & 24.00 & 0.68 \\
    $M_L+M_F+M_C$ & Robinson-Fould & ML & bla & bla & bla & bla \\
                  &                & Bayesian & no & 1167.40 & 124.00 & \textbf{0.00} \\
                  & Triples & ML & bla & bla & bla & bla \\
                  &         & Bayesian & no & 115.86 & 124.00 & 0.69 \\ 
    \hline
\label{Group_results}
\end{tabular}

@@

\begin{table}
\caption{$M_L$ non-parametric pairwise difference for Robinson-Fould metric}
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_L$00\% & $M_L$10\% & $M_L$25\% & $M_L$50\% & $M_L$75\% \\
    \hline
    $M_L$00\% & - & FALSE & \textbf{TRUE} & \textbf{TRUE} & \textbf{TRUE}\\
    $M_L$10\% & & - & FALSE & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$25\% & & & - & FALSE & \textbf{TRUE} \\
    $M_L$50\% & & & & - & FALSE \\
    $M_L$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_L$00\%-$M_L$10\% & 17.05 & 41.00 & FALSE \\ 
  $M_L$00\%-$M_L$25\% & 43.79 & 41.00 & TRUE \\ 
  $M_L$00\%-$M_L$50\% & 77.32 & 41.00 & TRUE \\ 
  $M_L$00\%-$M_L$75\% & 103.99 & 41.00 & TRUE \\ 
  $M_L$10\%-$M_L$25\% & 26.75 & 41.00 & FALSE \\ 
  $M_L$10\%-$M_L$50\% & 60.27 & 41.00 & TRUE \\ 
  $M_L$10\%-$M_L$75\% & 86.94 & 41.00 & TRUE \\ 
  $M_L$25\%-$M_L$50\% & 33.53 & 41.00 & FALSE \\ 
  $M_L$25\%-$M_L$75\% & 60.20 & 41.00 & TRUE \\ 
  $M_L$50\%-$M_L$75\% & 26.67 & 41.00 & FALSE \\ 
   \hline
\end{tabular}
\label{ML_results}
\end{table}

\begin{table}
\caption{$M_F$ non-parametric pairwise difference for Robinson-Fould metric in Bayesian framework}
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_F$00\% & $M_F$10\% & $M_F$25\% & $M_F$50\% & $M_F$75\% \\
    \hline
    $M_L$00\% & - & FALSE & FALSE & \textbf{TRUE} & \textbf{TRUE}\\
    $M_L$10\% & & - & FALSE & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$25\% & & & - & FALSE & \textbf{TRUE} \\
    $M_L$50\% & & & & - & FALSE \\
    $M_L$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_F$00\%-$M_F$10\% & 16.03 & 41.00 & FALSE \\ 
  $M_F$00\%-$M_F$25\% & 38.50 & 41.00 & FALSE \\ 
  $M_F$00\%-$M_F$50\% & 61.52 & 41.00 & TRUE \\ 
  $M_F$00\%-$M_F$75\% & 95.52 & 41.00 & TRUE \\ 
  $M_F$10\%-$M_F$25\% & 22.47 & 41.00 & FALSE \\ 
  $M_F$10\%-$M_F$50\% & 45.49 & 41.00 & TRUE \\ 
  $M_F$10\%-$M_F$75\% & 79.49 & 41.00 & TRUE \\ 
  $M_F$25\%-$M_F$50\% & 23.02 & 41.00 & FALSE \\ 
  $M_F$25\%-$M_F$75\% & 57.02 & 41.00 & TRUE \\ 
  $M_F$50\%-$M_F$75\% & 34.00 & 41.00 & FALSE \\ 
   \hline
\end{tabular}
\label{MF_results}
\end{table}

\begin{table}
\caption{$M_C$ non-parametric pairwise difference for Robinson-Fould metric in Bayesian framework}
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_C$00\% & $M_C$10\% & $M_C$25\% & $M_C$50\% & $M_C$75\% \\
    \hline
    $M_C$00\% & - & FALSE & FALSE & \textbf{TRUE} & \textbf{TRUE}\\
    $M_C$10\% & & - & FALSE & \textbf{TRUE} & \textbf{TRUE} \\
    $M_C$25\% & & & - & FALSE & \textbf{TRUE} \\
    $M_C$50\% & & & & - & FALSE \\
    $M_C$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_C$00\%-$M_C$10\% & 16.03 & 41.00 & FALSE \\ 
  $M_C$00\%-$M_C$25\% & 38.50 & 41.00 & FALSE \\ 
  $M_C$00\%-$M_C$50\% & 61.52 & 41.00 & TRUE \\ 
  $M_C$00\%-$M_C$75\% & 95.52 & 41.00 & TRUE \\ 
  $M_C$10\%-$M_C$25\% & 22.47 & 41.00 & FALSE \\ 
  $M_C$10\%-$M_C$50\% & 45.49 & 41.00 & TRUE \\ 
  $M_C$10\%-$M_C$75\% & 79.49 & 41.00 & TRUE \\ 
  $M_C$25\%-$M_C$50\% & 23.02 & 41.00 & FALSE \\ 
  $M_C$25\%-$M_C$75\% & 57.02 & 41.00 & TRUE \\ 
  $M_C$50\%-$M_C$75\% & 34.00 & 41.00 & FALSE \\ 
   \hline
\end{tabular}
\label{MC_results}
\end{table}

>>>>

%For a colour version of the draft to a search>replace '-BW'>''

@@

%Title
\noindent{\Large \bf Effect of missing data in matrices containing living and fossil taxa on topological accuracy}
%Alternative punch title: "Bayesian method fails to infer topology using matrices containing both living and fossil taxa"
%Alternative punch title: "Maximum Likelihood outperforms Bayesian for inferring topology from matrices containing both living and fossil taxa"
\bigskip

@@

\section{Results}
%Do the check for L00F00C00
\subsection{Building the trees}
When generating the matrices using seqgen and rTraitDisc algorithms with low evolutionary rate parameter ($\alpha$=0.5) we successfully generated evolutionary histories.
In Maximum Likelihood, support values ranged from 0 to 100 with a median of 38 ($1^st$ quartile = 14, $3^rd$ quartile = 72 - see \hyperref[supplementaries]{supplementaries}). % This is actually bad.
Using Bayesian inference, all the chains converged with a significant effective sample size (ASSD $<$ 0.01 and ESS $>>$ 200 for each tree).
Good enough phylogenetic signal.

%\subsection{Comparing topologies}
%Did it worked? See sub-matrices part. TO DO

@@

%10/06 - Missing 8 ML Chains

\subsubsection{Effect of $M_L$}
In Maximum Likelihood framework, the topological recovery quickly drops with the amount of missing data when using both metrics (see Table ~\ref{Group_results} - Fig. ~\ref{Fig_Results}).
However, this negative effect of missing data seems to stabilize beyond 25\% of missing data (no significant difference for trees with respectively 25\%, 50\% and 75\% missing living taxa).
With 10\% of missing living taxa, there is a different topological recovery depending on the used metric.
The Robinson-Fould metric shows a lower Tree similarity metric than the Triples metric meaning that individual taxa position are generally more conserved (i.e. low number of flying taxa) but that the full clades are less conserved (see Table ~\ref{NTS_ML_results}).

Howerver, topological recovery was bad in Bayesian, the tree similarity score was only slightly above 0 which means that the mode of the RPBTC was only slightly different than expected by chance (see Table ~\ref{NTS_Ba_results}).
However, it seems that there is a small difference depending on the metric used.
For the Triples metric there is no significant effect of the $M_L$ parameter, in other words, if living taxa are removed, there is no effect on the placement of "flying" taxa.
For the Robinson-Fould metric, there is a significant effect of the $M_L$ leading small decrease in topological recovery when $M_L$ increases.
In other words, if living taxa are removed, clades are less conserved (see Table ~\ref{Ba_RF-ML_results}).
However, in both cases, the effect of the parameter $M_L$ is still minimal compared to trees generated in a ML framework since the NTS score was only slightly higher than expected by chance (see Table ~\ref{Group_results} - Fig. ~\ref{Fig_Results}).

\subsubsection{Effect of $M_F$}
In Maximum Likelihood framework, the effect of missing data in the fossil record appeared to be constant and led to a constant decrease in topological recovery when the missing data increased (see Table ~\ref{Group_results} - Fig. ~\ref{Fig_Results}).
The difference between the two metrics used is more important than for the $M_L$ parameter: clades are less conserved than individual taxa placement as the amount of missing data increases.
Interestingly, 10\% or 25\% missing data for the $M_F$ parameter does not seems to affect the apparition of unstable taxa (Triples NTS modes of respectively 0.97 and 0.93 - Table ~\ref{NTS_ML_results}).

Similarly than for the effect of $M_L$, Bayesian tree recovery was only slightly better than expected by chance.
And in the same way as described above, there seems to be a small difference depending on the metric used.
There is no significant effect of the $M_F$ parameter when using the Triplet metric but the effect is significant when using the Robinson-Fould metric (see Table ~\ref{Ba_RF-MF_results}).
However, as mentioned previously the effect of the parameter $M_F$ is still minimal in a Bayesian framework (see Table ~\ref{Group_results} - Fig. ~\ref{Fig_Results}).

\subsubsection{Effect of $M_C$}
The number of missing morphological characters ($M_C$), however, seems to be more affecting topological recovery than $M_L$ and $M_F$ (see Table ~\ref{Group_results} - Fig. ~\ref{Fig_Results}).
The Robinson-Fould metric shows a rapid drop in tree recovery from 10\% of missing data (Robinson-Fould NTS mode $<$ to 0.5 from 10\% missing data - Table ~\ref{NTS_ML_results}).
This decrease is however slowlier when using the Triples metric with still a good topological recovery at 10\%  (Triples NTS modes = 0.95 - Table ~\ref{NTS_ML_results}).

The effect of $M_C$ in Bayesian framework is similar as the one described for $M_L$ and $M_F$: tree recovery is only slightly better than expected by chance and only the Robinson-Fould metric shows a significant effect of the $M_C$ parameter on tree recovery (see Table ~\ref{Ba_RF-ML_results} and ~\ref{Group_results} - Fig. ~\ref{Fig_Results}).

%\subsubsection{Combined effect}
%Need to do the heat plots

@@

%To sum up:
The ability of recovering the "best" tree's topology in maximum likelihood method is function of the amount of data missing.
The parameters $M_C$ and $M_L$ have more influence than $M_F$ on decrease in topological recovery.
The decrease in clade conservation (low Robinson-Fould NTS score) is faster than the increase in flying taxa (low Triples NTS score).
However, in Bayesian, topology is badly (if not at all) recovered disregarding the amount of data missing.

\begin{table}
\caption{Tree similarity values per parameter in ML framework}
\centering
\begin{tabular}{rrlccccc}
    \hline
    Parameter & amount of    & metric & mode & 50\%CI &       & 95\%CI &       \\
              & missing data &        &      & lower  & upper & lower  & upper \\
    \hline
    $M_L$     & 0\%          & Robinson-Fould & 1 & NA  & NA & NA  & NA \\
              &              & Triples        & 1 & NA  & NA & NA  & NA \\
              & 10\%         & Robinson-Fould & 0.671 & 0.569  & 0.789 & 0.468  & 1.036 \\ %how many digits?
              &              & Triples        & 0.942 & 0.868  & 0.999 & 0.612  & 1.063 \\
              & 25\%         & Robinson-Fould & 0.516 & 0.440  & 0.630 & 0.266  & 0.892 \\
              &              & Triples        & 0.559 & 0.708  & 0.810 & 0.291  & 0.999 \\
              & 50\%         & Robinson-Fould & 0.432 & 0.364  & 0.521 & 0.231  & 0.642 \\
              &              & Triples        & 0.514 & 0.419  & 0.599 & 0.293  & 0.910 \\
              & 75\%         & Robinson-Fould & 0.372 & 0.323  & 0.434 & 0.203  & 0.577 \\
              &              & Triples        & 0.444 & 0.338  & 0.532 & 0.192  & 0.855 \\
    $M_L$     & 0\%          & Robinson-Fould & 1 & NA  & NA & NA  & NA \\
              &              & Triples        & 1 & NA  & NA & NA  & NA \\
              & 10\%         & Robinson-Fould & 0.907 & 0.766  & 1.000 & 0.407  & 1.047 \\
              &              & Triples        & 0.976 & 0.944  & 1.003 & 0.715  & 1.104 \\
              & 25\%         & Robinson-Fould & 0.572 & 0.488  & 0.692 & 0.325  & 0.936 \\
              &              & Triples        & 0.937 & 0.820  & 0.993 & 0.539  & 1.086 \\
              & 50\%         & Robinson-Fould & 0.433 & 0.302  & 0.476 & 0.170  & 0.668 \\
              &              & Triples        & 0.732 & 0.594  & 0.873 & 0.341  & 1.025 \\
              & 75\%         & Robinson-Fould & 0.153 & 0.115  & 0.200 & 0.068  & 0.323 \\
              &              & Triples        & 0.458 & 0.390  & 0.611 & 0.290  & 0.856 \\   
    $M_L$     & 0\%          & Robinson-Fould & 1 & NA  & NA & NA  & NA \\
              &              & Triples        & 1 & NA  & NA & NA  & NA \\
              & 10\%         & Robinson-Fould & 0.473 & 0.384  & 0.835 & 0.356  & 0.958 \\
              &              & Triples        & 0.959 & 0.869  & 1.026 & 0.572  & 1.067 \\
              & 25\%         & Robinson-Fould & 0.454 & 0.357  & 0.630 & 0.242  & 0.916 \\
              &              & Triples        & 0.907 & 0.751  & 0.997 & 0.446  & 1.070 \\
              & 50\%         & Robinson-Fould & 0.424 & 0.375  & 0.466 & 0.249  & 0.828 \\
              &              & Triples        & 0.683 & 0.571  & 0.822 & 0.277  & 1.008 \\
              & 75\%         & Robinson-Fould & 0.230 & 0.177  & 0.302 & 0.108  & 0.567 \\
              &              & Triples        & 0.451 & 0.373  & 0.572 & 0.224  & 0.791 \\
    \hline
\label{NTS_ML_results}
\end{tabular}
\end{table}

\begin{table}
\caption{Tree similarity values per parameter in Bayesian framework}
\centering
\begin{tabular}{rrlccccc}
    \hline
    Parameter & amount of    & mode & 50\%CI &       & 95\%CI & \\
              & missing data &      & lower  & upper & lower  & upper \\
    \hline
    $M_L$     & 0\%          & Robinson-Fould & 0.056 & 0.035  & 0.063 & 0.031   & 0.076 \\ %how many digits?
              &              & Triples        & 0.041 & 0.008  & 0.054 & -0.039  & 0.106 \\
              & 10\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.028   & 0.061 \\
              &              & Triples        & 0.033 & 0.003  & 0.049 & -0.049  & 0.117 \\
              & 25\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.015   & 0.061 \\
              &              & Triples        & 0.035 & 0.002  & 0.049 & -0.041  & 0.096 \\
              & 50\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.015   & 0.056 \\
              &              & Triples        & 0.028 & 0.003  & 0.052 & -0.038  & 0.092 \\
              & 75\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.010   & 0.043 \\
              &              & Triples        & -0.001 & -0.018 & 0.040 & -0.060 & 0.106 \\
    $M_L$     & 0\%          & Robinson-Fould & 0.056 & 0.035  & 0.063 & 0.031   & 0.076 \\
              &              & Triples        & 0.041 & 0.008  & 0.054 & -0.039  & 0.106 \\
              & 10\%         & Robinson-Fould & 0.035 & 0.031  & 0.056 & 0.027   & 0.076 \\
              &              & Triples        & 0.026 & 0.002  & 0.050 & -0.046  & 0.105 \\
              & 25\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.0153  & 0.068 \\
              &              & Triples        & 0.038 & 0.002  & 0.050 & -0.046  & 0.105 \\
              & 50\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.015   & 0.058 \\
              &              & Triples        & 0.014 & -0.011 & 0.039 & -0.038  & 0.124 \\
              & 75\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.015   & 0.041 \\
              &              & Triples        & 0.029 & 0.019  & 0.042 & -0.030  & 0.089 \\   
    $M_L$     & 0\%          & Robinson-Fould & 0.056 & 0.035  & 0.063 & 0.031   & 0.076 \\
              &              & Triples        & 0.041 & 0.008  & 0.054 & -0.039  & 0.106 \\
              & 10\%         & Robinson-Fould & 0.056 & 0.035  & 0.059 & 0.0281  & 0.076 \\
              &              & Triples        & 0.030 & 0.011  & 0.048 & -0.024  & 0.094 \\
              & 25\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.023   & 0.076 \\
              &              & Triples        & 0.020 & -0.001 & 0.037 & -0.060  & 0.109 \\
              & 50\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.030   & 0.059 \\
              &              & Triples        & 0.010 & -0.005 & 0.045 & -0.036  & 0.104 \\
              & 75\%         & Robinson-Fould & 0.035 & 0.035  & 0.035 & 0.011   & 0.043 \\
              &              & Triples        & 0.024 & 0.001  & 0.042 & -0.037  & 0.104 \\
    \hline
\label{NTS_BA_results}
\end{tabular}
\end{table}

\begin{table}
\caption{Group difference per configuration set}
\centering
\begin{tabular}{rllcccc}
    \hline
    set & metric & framework & parametric & $stats^1$ & df & p.value \\
    \hline
    $M_L$         & Robinson-Fould & ML       & no & 151.438  & 4   & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 1.001278e-31
                  &                & Bayesian & no & 65.62    & 4   & \textbf{0.00} \\ 
                  & Triples        & ML       & no & 142.8329 & 4   & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains  - 6.983434e-30
                  &                & Bayesian & no & 4.56     & 4   & 0.34          \\ 
    $M_F$         & Robinson-Fould & ML       & no & 179.9238 & 4   & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 7.743067e-38
                  &                & Bayesian & no & 85.61    & 4   & \textbf{0.00} \\
                  & Triples        & ML       & no & 150.059  & 4   & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 1.977386e-31
                  &                & Bayesian & no & 3.01     & 4   & 0.56          \\
    $M_C$         & Robinson-Fould & ML       & no & 151.3818 & 4   & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 1.029428e-31
                  &                & Bayesian & no & 64.23    & 4   & \textbf{0.00} \\
                  & Triples        & ML       & no & 138.374  & 4   & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 6.290979e-29
                  &                & Bayesian & no & 26.13    & 24  & 0.35          \\
    $M_L+M_F$     & Robinson-Fould & ML       & no & 734.9213 & 24  & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 1.104542e-139
                  &                & Bayesian & no & 317.97   & 24  & \textbf{0.00} \\
                  & Triples        & ML       & no & 531.5558 & 24  & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 4.581065e-97
                  &                & Bayesian & no & 3.01     & 24  & 0.56          \\
    $M_L+M_C$     & Robinson-Fould & ML       & no & 542.3233 & 24  & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 2.619808e-99
                  &                & Bayesian & no & 290.10   & 24  & \textbf{0.00} \\
                  & Triples        & ML       & no & 437.7413 & 24  & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains -  1.28493e-77
                  &                & Bayesian & no & 22.19    & 24  & 0.57          \\
    $M_F+M_C$     & Robinson-Fould & ML       & no & 812.206  & 24  & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 5.463138e-156
                  &                & Bayesian & no & 385.96   & 24  & \textbf{0.00} \\
                  & Triples        & ML       & no & 528.9215 & 24  & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains - 1.619383e-96
                  &                & Bayesian & no & 20.23    & 24  & 0.68          \\ 
    $M_L+M_F+M_C$ & Robinson-Fould & ML       & no & 3603.808 & 124 & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains -3.819574e-169
                  &                & Bayesian & no & 1167.40  & 124 & \textbf{0.00} \\
                  & Triples        & ML       & no & 2047.923 & 124 & \textbf{0.00} \\ %10/06 - Missing 8 ML Chains 
                  &                & Bayesian & no & 115.86   & 124 & 0.69          \\
    \hline
\label{Group_results}
\end{tabular}

@@

\begin{table}
\caption{$M_L$ non-parametric pairwise difference for Robinson-Fould metric in ML framework} %10/06 - Missing 8 ML Chains
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_L$00\% & $M_L$10\% & $M_L$25\% & $M_L$50\% & $M_L$75\% \\
    \hline
    $M_L$00\% & - & \textbf{TRUE}  & \textbf{TRUE} & \textbf{TRUE} & \textbf{TRUE}\\
    $M_L$10\% & & - & \textbf{TRUE}  & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$25\% & & & - & FALSE  & \textbf{TRUE} \\
    $M_L$50\% & & & & - & FALSE  \\
    $M_L$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_L$00\%-$M_L$10\% & 56.53 & 37.66 & TRUE \\ 
  $M_L$00\%-$M_L$25\% & 96.85 & 37.66 & TRUE \\ 
  $M_L$00\%-$M_L$50\% & 127.03 & 37.66 & TRUE \\ 
  $M_L$00\%-$M_L$75\% & 144.58 & 37.66 & TRUE \\ 
  $M_L$10\%-$M_L$25\% & 40.31 & 37.66 & TRUE \\ 
  $M_L$10\%-$M_L$50\% & 70.50 & 37.66 & TRUE \\ 
  $M_L$10\%-$M_L$75\% & 88.05 & 37.66 & TRUE \\ 
  $M_L$25\%-$M_L$50\% & 30.19 & 37.66 & FALSE \\ 
  $M_L$25\%-$M_L$75\% & 47.73 & 37.66 & TRUE \\ 
  $M_L$50\%-$M_L$75\% & 17.55 & 37.66 & FALSE \\ 
   \hline
\end{tabular}
\label{ML_RF-ML_results}
\end{table}

\begin{table}
\caption{$M_L$ non-parametric pairwise difference for Triples metric in ML framework} %10/06 - Missing 8 ML Chains
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_L$00\% & $M_L$10\% & $M_L$25\% & $M_L$50\% & $M_L$75\% \\
    \hline
    $M_L$00\% & - & \textbf{TRUE}  & \textbf{TRUE} & \textbf{TRUE} & \textbf{TRUE}\\
    $M_L$10\% & & - & \textbf{TRUE}  & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$25\% & & & - & FALSE  & FALSE \\
    $M_L$50\% & & & & - & FALSE  \\
    $M_L$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_L$00\%-$M_L$10\% & 57.98 & 37.66 & TRUE \\ 
  $M_L$00\%-$M_L$25\% & 105.83 & 37.66 & TRUE \\ 
  $M_L$00\%-$M_L$50\% & 120.86 & 37.66 & TRUE \\ 
  $M_L$00\%-$M_L$75\% & 140.34 & 37.66 & TRUE \\ 
  $M_L$10\%-$M_L$25\% & 47.85 & 37.66 & TRUE \\ 
  $M_L$10\%-$M_L$50\% & 62.88 & 37.66 & TRUE \\ 
  $M_L$10\%-$M_L$75\% & 82.36 & 37.66 & TRUE \\ 
  $M_L$25\%-$M_L$50\% & 15.03 & 37.66 & FALSE \\ 
  $M_L$25\%-$M_L$75\% & 34.51 & 37.66 & FALSE \\ 
  $M_L$50\%-$M_L$75\% & 19.48 & 37.66 & FALSE \\ 
   \hline
\end{tabular}
\label{ML_Tr-ML_results}
\end{table}

\begin{table}
\caption{$M_L$ non-parametric pairwise difference for Robinson-Fould metric in Bayesian framework}
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_L$00\% & $M_L$10\% & $M_L$25\% & $M_L$50\% & $M_L$75\% \\
    \hline
    $M_L$00\% & - & FALSE & \textbf{TRUE} & \textbf{TRUE} & \textbf{TRUE}\\
    $M_L$10\% & & - & FALSE & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$25\% & & & - & FALSE & \textbf{TRUE} \\
    $M_L$50\% & & & & - & FALSE \\
    $M_L$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_L$00\%-$M_L$10\% & 17.05 & 41.00 & FALSE \\ 
  $M_L$00\%-$M_L$25\% & 43.79 & 41.00 & TRUE \\ 
  $M_L$00\%-$M_L$50\% & 77.32 & 41.00 & TRUE \\ 
  $M_L$00\%-$M_L$75\% & 103.99 & 41.00 & TRUE \\ 
  $M_L$10\%-$M_L$25\% & 26.75 & 41.00 & FALSE \\ 
  $M_L$10\%-$M_L$50\% & 60.27 & 41.00 & TRUE \\ 
  $M_L$10\%-$M_L$75\% & 86.94 & 41.00 & TRUE \\ 
  $M_L$25\%-$M_L$50\% & 33.53 & 41.00 & FALSE \\ 
  $M_L$25\%-$M_L$75\% & 60.20 & 41.00 & TRUE \\ 
  $M_L$50\%-$M_L$75\% & 26.67 & 41.00 & FALSE \\ 
   \hline
\end{tabular}
\label{Ba_RF-ML_results}
\end{table}

\begin{table}
\caption{$M_F$ non-parametric pairwise difference for Robinson-Fould metric in ML framework} %10/06 - Missing 8 ML Chains
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_F$00\% & $M_F$10\% & $M_F$25\% & $M_F$50\% & $M_F$75\% \\
    \hline
    $M_L$00\% & - & \textbf{TRUE} & \textbf{TRUE} & \textbf{TRUE} & \textbf{TRUE}\\
    $M_L$10\% & & - & FALSE & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$25\% & & & - & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$50\% & & & & - & \textbf{TRUE} \\
    $M_L$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_F$00\%-$M_F$10\% & 59.27 & 37.66 & TRUE \\ 
  $M_F$00\%-$M_F$25\% & 79.72 & 37.66 & TRUE \\ 
  $M_F$00\%-$M_F$50\% & 120.70 & 37.66 & TRUE \\ 
  $M_F$00\%-$M_F$75\% & 167.81 & 37.66 & TRUE \\ 
  $M_F$10\%-$M_F$25\% & 20.45 & 37.66 & FALSE \\ 
  $M_F$10\%-$M_F$50\% & 61.43 & 37.66 & TRUE \\ 
  $M_F$10\%-$M_F$75\% & 108.55 & 37.66 & TRUE \\ 
  $M_F$25\%-$M_F$50\% & 40.98 & 37.66 & TRUE \\ 
  $M_F$25\%-$M_F$75\% & 88.09 & 37.66 & TRUE \\ 
  $M_F$50\%-$M_F$75\% & 47.12 & 37.66 & TRUE \\ 
   \hline
\end{tabular}
\label{ML_RF-MF_results}
\end{table}
